Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-07 ms.tex
Modifying the windheating appendix

\documentclass[usenatbib,fleqn]{mn2e}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{hyperref}
\epstopdfsetup{outdir=./figures/}
\graphicspath{{./figures/}}
\usepackage{url}
\usepackage{aas_macros}
\usepackage{astro}
\usepackage{deluxetable}
% \usepackage{natbib}

@@

\begin{deluxetable}{lccccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{6}
\tabcolsep0.05in\footnotesize
\tablewidth{0pc}
\tablecaption{Results
\label{tab:surveys}}
\tablehead {
\colhead{Name}           &
\colhead{Ang.~Res.}  &
\colhead{$\nu$}          &
\colhead{F$_{\rm lim}^{(a)}$}               & 
\colhead{Area}          &
\colhead{$\Delta T$$^{(c)}$}            &
%\colhead{$T$$^{(d)}$}        &
\colhead{N$_{\rm obs}$$^{(e)}$}        &
\colhead{ref.}           
}
\startdata
\colhead{}           &
\colhead{(arcsec)}  &
\colhead{(GHz)}          &
\colhead{(mJy)}               & 
\colhead{(deg$^{2}$)}          &
\colhead{(d)}            &
%\colhead{(yr)}      &       
\colhead{}      \\
\hline
LOFAR & 80 & 0.15 & 11 & 1500 & 30 & 36 & 1\\
LOFAR-Expanded  & - & - & 1.1 & $10^{4}$  & 30  & 36 & -\\
VAST-Wide  & 10 & 1.3 & 0.5 & 10$^{4}$ & 1   & 1096 & 2\\
VAST-Deep & - & - & 0.05 & -  & 365  & 4 & - \\
VAST-Deep Single Field & - & - & - & -  & 1  & 365 & - \\
VLASS-Wide  & 2 & 3 & 0.1 & $10^{4}$ & 365  & 4 & - \\
VLASS-Deep  & 0.6 & - & 0.003 & 10  & 365  & 4 & - \\
%VLASS-Deep-Short  & - & - & 0.01 & 40  & 10  & 10 & - \\
%CMB50cm  & 840 & 150 & 3.2 & 10$^{4}$  & 1  & 1096 & - \\
%CMB2m  & - & - & 1.0 & -  & -  & - & - \\
CMB-fast  & 840 & 150 & 1.0 & 10$^{4}$  & 1  & 1096 & - \\
CMB-deep  & - & - & 0.1 & -  & 100  & 11 & - \\
\enddata
\tablecomments{Put Results Here}
\end{deluxetable}

@@

We estimate the importance of Compton heating by assuming the SMBH radiates with a luminosity $L = \epsilon \dot{M}c^{2}$, where $\epsilon$ is the radiative efficiency and where $\dot{M}$ is estimated from equation (\ref{eq:mdot_analytic}).  Then using equations (\ref{eq:rs_simple}), (\ref{eq:mdot_analytic}), (\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate that from equation (\ref{eq:vw_eff}) that
\begin{align}
v_{\rm w,0}^{\rm C}  \simeq
  \begin{cases}
   13 \eta_{0.02}^{0.5}T_{\rm C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.38}v_{500}^{-1.4}\,{\rm km\,s^{-1}}  &, \text{core}\\
   20 \eta_{0.02}^{0.5}T_{\rm C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.24}v_{500}^{-0.7}\,{\rm km\,s^{-1}}   &, \text{cusp},     
  \end{cases}
  \label{eq:vC}
\end{align}
where $T_{C,9} = T_{C}/10^{9}$ K and $\epsilon_{-2} = \epsilon/0.01 \sim 1$ is the maximum radiative efficiency for a thick accretion flow (e.g.~\citealt{Narayan&Yi95}).  Assuming that heating is dominated by Compton heating ($v_{w} = v_{\rm w,0}^{C}$) one finds that
\begin{align}
v_{\rm w,0}^{\rm C}  \simeq
  \begin{cases}
   106 \eta_{0.02}^{0.21}T_{\rm C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}  &, \text{core}\\
   76 \eta_{0.02}^{0.29}T_{\rm C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}   &, \text{cusp},     
  \end{cases}
  \label{eq:vC2}
\end{align}
Unless $\eta$ is very high, we conclude that Compton heating is insufficient to stabilize the steady flow against cooling instability (e.g. $v_{\rm w,0}^{C} < v_{\rm critt}$; eq.~[\ref{eq:cooling2}]).

@@

% Note that we have two free parameters ($\eta$ and $\vwO$) in our
% model, which implies that we can always match the observed temperature
% and densities at at least one point.  As a general rule, we find that
% a wind heating parameter $\vwO=500$ km s$^{-1}$ gives rough agreement
% with the observed temperatures.  We now highlight results for specific
% galaxies.
% % Thus, we choose $\vwO=500$ km/s.  We choose an
% % $\eta$ so that our solution would be consistent with the observed
% % density profiles. The comparison is shown in
% %% AG-The chosen properties, in particular eta may be summarized in a table.
% %% AG-Mention rising temperature profiles on large scales.

>>>>

\documentclass[usenatbib,fleqn]{mn2e}
\usepackage{amsmath,amssymb}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{hyperref}
\epstopdfsetup{outdir=./figures/}
\graphicspath{{./figures/}}
\usepackage{url}
\usepackage{aas_macros}
\usepackage{astro}
\usepackage{deluxetable}
% \usepackage{natbib}

@@

\begin{deluxetable}{lllllll}
\tabletypesize{\scriptsize}
\tabcolsep0.05in\footnotesize
\tablewidth{0pc}
\tablecaption{Cusp Results
\label{tab:sols}}
\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w,0}$} &
  \colhead{$\gamma$} & \colhead{$r_b$} &
  \colhead{$\dot{M}/\dot{M}_{\rm Edd}$} & \colhead{$t_{\rm
      cool}/t_{\rm ff} (r_s)$} & \colhead{comments}}
\startdata
0.01 & 300.0 & 0.8 & 100.0 & $ 3.2 \times 10^{ -4 }$ & 4.7 & rb in fact
unresolved \\
0.01 & 600.0 & 0.8 & 100.0 & $ 5.5 \times 10^{ -5 }$ & $ 3.2 \times
10^{ 2 }$ &  rb in fact unresolved\\
0.01 & 1200.0 & 0.8 & 100.0 & $ 9.4 \times 10^{ -6 }$ & $ 1.5 \times
10^{ 4 }$ &  rb in fact unresolved\\
0.1 & 300.0 & 0.8 & 100.0 & $ 2.5 \times 10^{ -3 }$ & 0.29 & energy
cons on outer grid \\
0.1 & 600.0 & 0.8 & 100.0 & $ 1.8 \times 10^{ -4 }$ & 97 &  \\
0.1 & 1200.0 & 0.8 & 100.0 & $ 3.1 \times 10^{ -5 }$ & $ 4.8 \times
10^{ 3 }$ &  energy cons on inner grid\\
1 & 300.0 & 0.8 & 100.0 & $ 1.6 \times 10^{ -2 }$ & $ 5.6 \times 10^{ -2 }$ &  \\
1 & 600.0 & 0.8 & 100.0 & $ 7.3 \times 10^{ -4 }$ & 21 &  \\
1 & 1200.0 & 0.8 & 100.0 & $ 9.9 \times 10^{ -5 }$ & $ 1.5 \times 10^{ 3 }$ &  \\
0.1 & 300.0 & 0.8 & 50.0 & $ 2.0 \times 10^{ -3 }$ & 0.46 &  \\
0.1 & 300.0 & 0.8 & 300.0 & $ 7.2 \times 10^{ -3 }$ & $ 6.7 \times 10^{ -2 }$ &  \\
0.1 & 300.0 & 0.8 & 200.0 & $ 5.3 \times 10^{ -3 }$ & 0.12 &  \\
0.1 & 300.0 & 0.8 & 400.0 & $ 8.9 \times 10^{ -3 }$ & $ 4.7 \times 10^{ -2 }$ &  \\
1 & 300.0 & 0.8 & 50.0 & $ 8.2 \times 10^{ -3 }$ & 0.19 &  \\
1 & 300.0 & 0.8 & 200.0 & $ 3.6 \times 10^{ -2 }$ & $ 1.7 \times 10^{ -2 }$ &  \\
1 & 300.0 & 0.8 & 300.0 & $ 5.2 \times 10^{ -2 }$ & $ 9.8 \times 10^{
  -3 }$ &  rb=400 pc was unsuccessful\\
\enddata
\end{deluxetable}

\begin{deluxetable}{lllllll}
\tabletypesize{\scriptsize}
%\tablecolumns{6}
\tabcolsep0.05in\footnotesize
\tablewidth{0pc}
\tablecaption{Core Results \label{tab:sols}}
\tablehead{\colhead{$M_{\bullet,8}$} & \colhead{$v_{w,0}$} &
\colhead{$\gamma$} & \colhead{$r_b$} & \colhead{$\dot{M}/\dot{M}_{\rm
Edd}$}  & \colhead{$t_{\rm cool}/t_{\rm ff} (r_s)$} & \colhead{comments}}
\startdata
0.01 & 600.0 & 0.1 & 100.0 & $ 3.4 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 2 }$ &  \\
0.01 & 1200.0 & 0.1 & 100.0 & $ 1.5 \times 10^{ -6 }$ & $ 4.1 \times 10^{ 4 }$ &  \\
0.1 & 1200.0 & 0.1 & 100.0 & $ 9.5 \times 10^{ -6 }$ & $ 5.7 \times 10^{ 3 }$ &  \\
1 & 1200.0 & 0.1 & 100.0 & $ 6.0 \times 10^{ -5 }$ & $ 8.6 \times 10^{ 2 }$ &  \\
1 & 1200.0 & 0.1 & 300.0 & $ 1.9 \times 10^{ -4 }$ & $ 1.3 \times 10^{ 2 }$ &  \\
\enddata
\end{deluxetable}

@@

{\bf AG: Note that I obtain Compton heating which is a factor of 2
  higher--although power law dependences look right to me. Note that
  the Compton heating will depend on radius--I use rs in my own
  estimate. }
We estimate the importance of Compton heating by assuming the SMBH
radiates with a luminosity $L = \epsilon \dot{M}c^{2}$, where
$\epsilon$ is the radiative efficiency and where $\dot{M}$ is
estimated from equation (\ref{eq:mdot_analytic}).  Then using
equations (\ref{eq:rs_simple}), (\ref{eq:mdot_analytic}),
(\ref{eq:rhors}), (\ref{eq:rhostarrs}) we calculate that from equation
(\ref{eq:vw_eff}) that
\begin{align} v_{\rm w,0}^{\rm C} \simeq
  \begin{cases} 13 \eta_{0.02}^{0.5}T_{\rm
C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.38}v_{500}^{-1.4}\,{\rm
km\,s^{-1}} &, \text{core}\\ 20 \eta_{0.02}^{0.5}T_{\rm
C,9}^{0.5}\epsilon_{-2}^{0.5} M_{\bullet,8}^{0.24}v_{500}^{-0.7}\,{\rm
km\,s^{-1}} &, \text{cusp},
  \end{cases}
  \label{eq:vC}
\end{align} where $T_{C,9} = T_{C}/10^{9}$ K and $\epsilon_{-2} =
\epsilon/0.01 \sim 1$ is the maximum radiative efficiency for a thick
accretion flow (e.g.~\citealt{Narayan&Yi95}).  Assuming that heating
is dominated by Compton heating ($v_{w} = v_{\rm w,0}^{C}$) one finds
that
\begin{align} v_{\rm w,0}^{\rm C} \simeq
  \begin{cases} 106 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 76 \eta_{0.02}^{0.29}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align} Unless $\eta$ is very high, we conclude that Compton
heating is insufficient to stabilize the steady flow against cooling
instability (e.g. $v_{\rm w,0}^{C} < v_{\rm critt}$;
eq.~[\ref{eq:cooling2}]).

@@

% Note that we have two free parameters ($\eta$ and $\vwO$) in our
% model, which implies that we can always match the observed temperature
% and densities at at least one point.  As a general rule, we find that
% a wind heating parameter $\vwO=500$ km s$^{-1}$ gives rough agreement
% with the observed temperatures.  We now highlight results for specific
% galaxies.
% % Thus, we choose $\vwO=500$ km/s.  We choose an
% % $\eta$ so that our solution would be consistent with the observed
% % density profiles. The comparison is shown in
% %% AG-The chosen properties, in particular eta may be summarized in a tabe.
% %% AG-Mention rising temperature profiles on large scales.

### 2015-01-07 windheat.tex
Modifying the windheating appendix

If we assume that a stellar population forms
impulsively in the distant pass with IMF $\mu(m_*)$(with minimum mass
$m_0$ and maximum mass $m_1$), then the surviving mass fraction at any
future time $t$ is given by
\begin{equation}
f(t) =\frac{ \int_{m_0}^{m_{\rm T}(t)} m_* \mu(m_*) dm_* }{ \int_{m_0}^{m_1} m_* \mu(m_*) dm_* },
\end{equation}
where the main sequence turnoff mass is approximately
\begin{equation}
m_{\rm T}(t) \approx 2.5M_\odot~ \left( \frac{t}{10^9~{\rm yr}} \right)^{-0.4}.
\end{equation}
For a Salpeter IMF $\mu(m_*) \propto m_*^{-2.35}$ with $m_0=0.1M_\odot$ and $m_1=100M_\odot$,
\begin{equation}
f_{\rm Sal}(t) = 1.098 - 0.490 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{0.14}
\end{equation}
{\bf NCS: we should probably use a Kroupa/Chabrier IMF, but this gets the ball rolling.}
If we approximate post-main sequence evolution as instantaneous and define $\lambda(m_*)$ as the fractional mass lost during all stages of stellar evolution, then the mass loss rate density
\begin{equation}
q(t) = \frac{\rho_*}{\bar{m}_*} \lambda(m_{\rm T}(t)) m_{\rm T}(t) \frac{df}{dt},
\end{equation}
where the mean stellar mass $\bar{m}_* = \int_{m_0}^{m_{\rm T}(t)} m_*\mu(m_*)dm_* \approx 0.3 M_\odot$.  Further approximating $\lambda(m_*)=0.5$, and using the Salpeter IMF once more, gives
\begin{equation}
q(t) = \frac{\rho_*}{10^{10}~{\rm yr}} \times 0.11 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{-1.26}.
\end{equation}
This is a specific, time-dependent definition of $\eta(t) (=0.11(t/t_{\rm h})^{-1.26})$; if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.  Once these free parameters are specified, however, we can answer an important question: do young stellar populations increase or decrease the SMBH feeding rate $\dot{M}$?  Clearly, $\eta(t)$ is larger for young stellar populations, but these stars also have high wind velocities that diminish the stagnation radius.  Crudely approximating $v_{\rm w}=75~{\rm km~s}^{-1}$ for $m_{\rm T} < 10M_{\odot}$ and $v_{\rm w}=3000~{\rm km~s}^{-1}$ for $m_{\rm T} > 10M_{\odot}$ (motivated by the transition from dust-driven wind loss on the AGB to line-driven wind loss from Wolf-Rayet stars), we can employ the relation $\dot{M} \propto \eta(t) r_{\rm s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_* \propto r^{-\Gamma}$) to determine the impact of stellar ``youth'' on SMBH feeding rates.
{\bf AG:As I previously mentioned this discussion of the eta is not
  quite correct...}
\begin{figure}
\includegraphics[width=\columnwidth]{NickPlot.eps}
\caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times M_*(r_{\rm s})$, in arbitrary units.  The green, blue, and black curves are for galaxies with $\Gamma$ values of $0.1$, $0.5$, and $0.9$, respectively.  Solid curves represent impulsive-mode star formation, while dotted curves represent continuous-mode star formation. {\bf NCS: I think these old continuous curves are wrong, need to revise}}
\end{figure}

In Fig. \ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a
function of time, for three different stellar density profiles $\Gamma
= \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an
influence radius $r _{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$
SMBH).  We parametrize the wind velocity as
\begin{equation} \frac{v_{\rm w}}{3000 ~\rm
km~s^{-1}}=520-495\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm
yr}}\right). \label{NickV1}
\end{equation} This counts Type II SNe heating as ``winds;'' if
instead we are in the portion of parameter space where $r_{\rm II}$ is
very large, then we use the alternate parametrization
\begin{equation} \frac{v_{\rm w}}{3000 ~\rm
km~s^{-1}}=520-495\tanh\left( \frac{t-10^{7}~{\rm yr}}{10^{6.5}~{\rm
yr}}\right), \label{NickV2}
\end{equation} which only allows short lived Wolf-Rayet stars to
contribute to the high-heating mode.  The ``impulsive burst'' mode of
star formation produces large ($\sim 10$) differences between the
three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but
smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is
large.  We also plot, as dotted curves, a simple model for the
``continuous'' mode of star formation, where mass loss is calculated
as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average
energy injection in the wind is calculated as $\bar{v_{\rm
w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm
km~s}^{-1})^2$.  Interestingly, the continuous mode of star formation
produces small differences from late-time $\dot{M}$ seen in cusp
galaxies with impulsive star formation; however, continuous mode star
formation decreases late-time $\dot{M}$ by an order of magnitude
relative to impulsive star formation in core galaxies.  {\bf NCS: I
think this old discussion of MDot in the continuous limit is wrong,
need to revise}

The continuous mode of star formation can be studied more accurately
by including arbitrary star formation histories $S(t)$, measured in
units of mass per time.  In particular, if an impulsively formed
stellar population that is $t$ years of age, we can write its current
mass loss rate, $\dot{\bar{m}}(t)$, and its current effective wind
speed, $\bar{v}_{\rm w}(t)$.  Specifically,
\begin{align} 
  \dot{\bar{m}}(t) &= \frac{\Delta M(t) \mu(M_{\rm TO}(t))
    \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm ms} \int_{m_0}^{m_{\rm
        T}(t)}
    \dot{m}(m_*, t) \mu(m_*) {\rm d}m_* }{\bar{m}_*}\\
  \dot{\bar{e}}(t) &=\dot{e}_{\rm TO}+ f_{\rm MS} \int_{m_0}^{m_{\rm T}(t)}
  \frac{\vw^2(t) \dot{m}(m_*, t) \mu(m_*) {\rm d}m_*}{\bar{m}_*}.
\end{align}

The first term corresponds to a more impulsive contribution from
post-main sequence (PMS) stars, while the second term corresponds to
the contribution from main-sequence winds.

{\bf Note that I have not written the turnoff contribution in terms of
  a wind velocity. One can simply read off the specific energy
  injection rate from Voss '09...}

@@

\begin{align}
\bar{v}_w=2 \dot{\bar{e}}/\dot{\bar{m}}
\end{align}

We can then use these integrated quantities to determine the effective
$V_w$ for arbitrary star formation histories.

>>>>

% If we assume that a stellar population forms
% impulsively in the distant pass with IMF $\mu(m_*)$(with minimum mass
% $m_0$ and maximum mass $m_1$), then the surviving mass fraction at any
% future time $t$ is given by
% \begin{equation}
% f(t) =\frac{ \int_{m_0}^{m_{\rm T}(t)} m_* \mu(m_*) dm_* }{ \int_{m_0}^{m_1} m_* \mu(m_*) dm_* },
% \end{equation}
% where the main sequence turnoff mass is approximately
% \begin{equation}
% m_{\rm T}(t) \approx 2.5M_\odot~ \left( \frac{t}{10^9~{\rm yr}} \right)^{-0.4}.
% \end{equation}
% For a Salpeter IMF $\mu(m_*) \propto m_*^{-2.35}$ with $m_0=0.1M_\odot$ and $m_1=100M_\odot$,
% \begin{equation}
% f_{\rm Sal}(t) = 1.098 - 0.490 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{0.14}
% \end{equation}
% {\bf NCS: we should probably use a Kroupa/Chabrier IMF, but this gets the ball rolling.}
% If we approximate post-main sequence evolution as instantaneous and define $\lambda(\Mstar)$ as the fractional mass lost during all stages of stellar evolution, then the mass loss rate density
% \begin{equation}
% q(t) = \frac{\rho_*}{\bar{m}_*} \lambda(m_{\rm T}(t)) m_{\rm T}(t) \frac{df}{dt},
% \end{equation}
% where the mean stellar mass $\bar{m}_* = \int_{m_0}^{m_{\rm T}(t)} \Mstar\mu(\Mstar)d\Mstar \approx 0.3 M_\odot$.  Further approximating $\lambda(\Mstar)=0.5$, and using the Salpeter IMF once more, gives
% \begin{equation}
% q(t) = \frac{\rho_*}{10^{10}~{\rm yr}} \times 0.11 \left(\frac{t}{10^{10}~{\rm yr}} \right)^{-1.26}.
% \end{equation}
% This is a specific, time-dependent definition of $\eta(t) (=0.11(t/t_{\rm h})^{-1.26})$; if we consider different star formation scenarios (for example, continuous star formation) or different IMFs, it will change.  Once these free parameters are specified, however, we can answer an important question: do young stellar populations increase or decrease the SMBH feeding rate $\dot{M}$?  Clearly, $\eta(t)$ is larger for young stellar populations, but these stars also have high wind velocities that diminish the stagnation radius.  Crudely approximating $v_{\rm w}=75~{\rm km~s}^{-1}$ for $m_{\rm T} < 10M_{\odot}$ and $v_{\rm w}=3000~{\rm km~s}^{-1}$ for $m_{\rm T} > 10M_{\odot}$ (motivated by the transition from dust-driven wind loss on the AGB to line-driven wind loss from Wolf-Rayet stars), we can employ the relation $\dot{M} \propto \eta(t) r_{\rm s}^{2-\Gamma}\propto \eta(t) v_{\rm w}^{-4+2\Gamma}$ (where $\rho_* \propto r^{-\Gamma}$) to determine the impact of stellar ``youth'' on SMBH feeding rates.
% {\bf AG:As I previously mentioned this discussion of the eta is not
%   quite correct...}
% \begin{figure}
% \includegraphics[width=\columnwidth]{NickPlot.eps}
% \caption{\label{NickPlot} SMBH feeding rates $\dot{M}=\eta(t) \times \Mstar(r_{\rm s})$, in arbitrary units.  The green, blue, and black curves are for galaxies with $\Gamma$ values of $0.1$, $0.5$, and $0.9$, respectively.  Solid curves represent impulsive-mode star formation, while dotted curves represent continuous-mode star formation. {\bf NCS: I think these old continuous curves are wrong, need to revise}}
% \end{figure}

% In Fig. \ref{NickPlot} we plot $\dot{M}$, in arbitrary units, as a
% function of time, for three different stellar density profiles $\Gamma
% = \{1.1, 1.5, 1.9\}$ (which are normalized to have the same mass at an
% influence radius $r _{\rm soi}=10~{\rm pc}$ around a $10^7M_\odot$
% SMBH).  We parametrize the wind velocity as
% \begin{equation} \frac{v_{\rm w}}{3000 ~\rm
% km~s^{-1}}=520-495\tanh\left( \frac{t-10^{7.5}~{\rm yr}}{10^{7}~{\rm
% yr}}\right). \label{NickV1}
% \end{equation} This counts Type II SNe heating as ``winds;'' if
% instead we are in the portion of parameter space where $r_{\rm II}$ is
% very large, then we use the alternate parametrization
% \begin{equation} \frac{v_{\rm w}}{3000 ~\rm
% km~s^{-1}}=520-495\tanh\left( \frac{t-10^{7}~{\rm yr}}{10^{6.5}~{\rm
% yr}}\right), \label{NickV2}
% \end{equation} which only allows short lived Wolf-Rayet stars to
% contribute to the high-heating mode.  The ``impulsive burst'' mode of
% star formation produces large ($\sim 10$) differences between the
% three $\dot{M}$ curves at early times, when $r_{\rm s}$ is small, but
% smaller ($\sim 3$) differences at late times, when $r_{\rm s}$ is
% large.  We also plot, as dotted curves, a simple model for the
% ``continuous'' mode of star formation, where mass loss is calculated
% as $\bar{\eta} = \int\eta(t)dt/t_{\rm h} \approx 4$ and an average
% energy injection in the wind is calculated as $\bar{v_{\rm
% w}^2}=\int\eta(t)v_{\rm w}^2(t)dt/\bar{\eta} \approx (800~{\rm
% km~s}^{-1})^2$.  Interestingly, the continuous mode of star formation
% produces small differences from late-time $\dot{M}$ seen in cusp
% galaxies with impulsive star formation; however, continuous mode star
% formation decreases late-time $\dot{M}$ by an order of magnitude
% relative to impulsive star formation in core galaxies.  {\bf NCS: I
% think this old discussion of MDot in the continuous limit is wrong,
% need to revise}

The energy and mass injection from stellar winds will be the sum ofthe
contributions from main sequence and post-main sequence (PMS) stars.
For an impulsively formed stellar population of age $t$, the mass
injection rate per unit stellar mass ($\dot{\bar{m}}(t)$) and energy
injection rate per unit stellar mass will be given by
($\dot{\bar{e}}(t)$).

\begin{align} 
  \dot{\bar{m}}(t) &= \frac{\Delta M(t) \mu(M_{\rm TO}(t))
    \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm MS} \int_{m_0}^{m_{\rm
        T}(t)}
    \dot{m}(\Mstar, t) \mu(\Mstar) {\rm d}\Mstar }{\bar{m}_*}\\
  \dot{\bar{e}}(t) &=\dot{e}_{\rm TO}(t)+ f_{\rm MS} \int_{m_0}^{m_{\rm T}(t)}
  \frac{\vw^2(\Mstar, t) \dot{m}(\Mstar, t) \mu(\Mstar) {\rm d}\Mstar}{\bar{m}_*}.
  \label{eq:edotImp}
\end{align}

The first terms in each expression above correspond to the
contributions from PMS stars, while the second terms correspond to the
contributions from main sequence stars. The main sequence winds are
subdominant in mass, and may be not be thermalized and
mixed with the rest of the injected gas. Thus, we include a
thermalization efficiency, $ 0\le f_{\rm MS}\le 1$, in
equation~\eqref{eq:edotImp}. Throughout this paper we set $f_{\rm
  MS}=1$.

We assume a Salpeter IMF $\mu(\Mstar)\sim M^{-2.35}$, truncated at $0.1
\Msun$ on the low mass end and at $100 \Msun$ on the high mass
end. The corresponding $\bar{m}_*$ is 0.35 $\Msun$.

For the turnoff mass, $M_{\rm TO}$, we take the following fitting
formula

\begin{align}
\log(M_{\rm TO})=0.24 + 0.068 x^2-0.34 x+4.76 e^{-4.58 x},
\end{align}

where $x=\log(t/10^9 {\rm years})$ and $M_{\rm TO}$ is in units
$\Msun$. This fit is designed to reproduce the results in 
Table 9 of \citet{MaederMeynet:1987a} and then asymptotes to the fit
for $M_{\rm TO}$ given in equation (9) of \citet{CiottiOstriker:2007a}
for intermediate and late times ($t \gsim 10^8$ years).

For $\Delta M(t)$ we use equation (10) from \citet{CiottiOstriker:2007a}

\begin{align}
\Delta M=
\begin{cases}
0.945 M_{\rm TO}-0.503 & M_{\rm TO} < 9 \Msun\\
 M_{\rm TO}-1.4 \Msun &  M_{\rm TO} \ge 9 \Msun
\end{cases}
\end{align}

To estimate the mass loss from main sequence stars $\dot{\Mstar,t}$,
we use equation 4 \citet{SchroderCuntz:2005a}\footnote{This
  prescription is a generalization of the Reimers' mass loss law. This
expression is derived assuming the stellar wind results from the
turbulent overflow of moaterial in the chromosphere or underneath it.} {\bf AG:
  unfortunately this is not really meant for MS stars...}

\begin{align}
  \dot{m}(\Mstar)=8 \times 10^{-14} \frac{L_* R_*}{\Mstar}
  \left(\frac{T_{\rm eff}}{\rm 4000 K}\right)^{3.5}
  \left(1+\frac{g_{\odot}}{4300 g_*}\right) \Msun \pyear,\
\end{align}

where  $R_*$, $L_*$, $T_{\rm eff}$ and $g_*$ are the stellar radius,
luminosity, effective and surface gravity respectively. $g_{\odot}$ is
the stellar surface gravity. To calculate $R_*$ and $L_*$ we use the
following scaling relations (taken from Kippenhann and Weygert Figures
22.2 and 22.3).

\begin{align}
L_*=
\begin{cases}
L_{\odot} (\Mstar/\Msun)^{3.2} & \Mstar > \Msun \\
L_{\odot} (\Mstar/\Msun)^{2.5} & \Mstar \le \Msun
\end{cases}
\end{align}

\begin{align}
r_*=
\begin{cases}
R_{\odot} (\Mstar/\Msun)^{0.57} & \Mstar > \Msun \\
R_{\odot} (\Mstar/\Msun)^{0.8} & \Mstar \le \Msun
\end{cases}
\end{align}

To get a handle on $\dot{e}_{\rm TO}(t)$, we use the results from
\citet{VossDiehl+:2009a} who use a population synthesis code to
simulate the mass and energy injection into the ISM from an OB
association. For the first $\sim 10$ Myr the energy injection will
come from energetic Wolf-Rayet star winds. The energy injection rate
per massive star ($\Mstar>8 \Msun$), $\dot{\mathcal{E}} (t)$, from
stellar winds is plotted in the top panel of their Figure 7 and is
well fit {\bf AG: A little more detail here...} by

\begin{align}
\dot{\mathcal{E}} (t)=
\begin{cases}
  1.3 \times 10^{36} {\rm ergs/s} & t<4 \times 10^6 {\rm years}\\
  1.3  \times 10^{36} {\rm ergs/s} \left(\frac{t}{4 \times  10^6}\right)^{-3.73} & t \ge 4 \times 10^6 {\rm years}.
\end{cases}
\label{eq:voss}
\end{align}

 $\dot{e}_{\rm TO}(t)$ is related to $\dot{\mathcal{E}}$  via

\begin{align}
\dot{e}_{\rm TO}(t)=f_{8} \dot{\mathcal{E}} / \bar{m}_*,
\label{eq:eto}
\end{align}

where $f_{8}$ is the fraction of the stellar population with
$\Mstar>8 \Msun$. $f_8=2.6 \times 10^{-3}$ for our assumed Salpeter
IMF.  Equation~\eqref{eq:voss} and~\eqref{eq:eto} will be valid onlyfor $t
\lsim 10$ Myr. However, the turnoff contribution will become extremely
energetically subdominant at later times as far slower dust-driven
winds come to dominate the energy budget {\bf AG: Nick check--is the
  preceding sentence accurate}

We calculate the wind velocity for main sequence winds $v_w (\Mstar,
t)$ using...{\bf AG:Current just use the value for the sun~430 km/s
  replace with the real prescription we end up using.}

@@

\begin{align}
\bar{v}_w(t)=2 \dot{\bar{e}}(t)/\dot{\bar{m}}(t)
\label{eq:vwImp}
\end{align}

We plot $\bar{v}_w$ in Figure~\ref{fig:vwImp}.

\begin{figure}
\includegraphics[width=\columnwidth]{vwImp.pdf}
\caption{\label{fig:vwImp} The effective $\vw$ from stellar winds from
  a stellar population formed in a starburst $t$ years ago.}
\end{figure}

We can then use these integrated quantities to determine the effective
$V_w$ for arbitrary star formation histories. For a stellar population
with star formation rate $S(t)$
